Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-06 Manuscript/manuscript.tex
Table with gammas and ratios of binding to phos/carbonyl filled with values now.

Since artifacts were reported in simulations with \AA{}qvist ions is water \cite{auffinger07},
we also simulated the Lipid14 model with more realistic ion models by Dang et al.~\cite{smith94,chang1999,dang2006}, and
ECC-ions~\cite{jungwirth17-new-paper-to-be-published, Pluharova2014}. 
However, we still observed overestimated binding for both \ce{Ca^{2+}} and Na$^+$ with these ions models 
(Figs.~\ref{fig:delta_ordPar_CaCl} and~\ref{fig:delta_ordPar_NaCl}). 
\todo{Add OP-response of Lipid14+ECC-ions plot in SI}.
The results are in line with the previous work \cite{catte16},
suggesting that additional improvements in the lipid parameters are
required to correctly describe the binding of cations to phospholipid bilayers.

@@

\begin{table}[tb!]
  \caption{Relative surface excess of calcium with respect to water, 
  and the ratios of the amount of calcium cations 
  bound to phosphate or carbonyl moieties 
  to the amount of such cations bound to both moieties in a POPC bilayer 
  from various simulation models. 
  The CaCl$_2$ concentration of the ions in water before adsorption to the phospholipid bilayer
  is 350mM in the analyzed systems. \label{tab:binding}}
  \todo{Add columns with concentrations of calcium -- bulk/molar fraction.}
  \todo{Changing symbol $P$ to $R$ or $r$ might reflect better that it is rather a ratio, and not that much a probability.}
  \begin{tabular}{l|c c c}
    model                 & $\Gamma_{Ca}^w$ (nm$^{-2}$)   & $P^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ & $P^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} $ \\
    \hline
    ECC-lipids            &  $0.06 \pm 0.01 $            &  99\%   &    25\%    \\
    Lipid14/\AA{}qvist    &  $0.13 \pm 0.01 $            &  -       &     -       \\
    Lipid14/Dang          &  $0.23 \pm 0.03 $            &  -        &    -       \\
    Lipid14/ECC-ions      &  $0.35 \pm 0.11 $            &  -        &    -       \\
  \end{tabular}
\end{table}

>>>>

Since artifacts were reported in simulations with \AA{}qvist ions is water \cite{auffinger07},
we also simulated the Lipid14 model with more realistic ion models by Dang et al.~\cite{smith94,chang1999,dang2006}, and
ECC-ions~\cite{jungwirth17-new-paper-to-be-published, Pluharova2014}. 
However, we still observed overestimated binding for both \ce{Ca^{2+}} and Na$^+$ with these ions models 
(Figs.~\ref{fig:delta_ordPar_CaCl} and~\ref{fig:delta_ordPar_NaCl}). 
The results are in line with the previous work \cite{catte16},
suggesting that additional improvements in the lipid parameters are
required to correctly describe the binding of cations to phospholipid bilayers.

@@

\begin{table}[tb!]
  \caption{Relative surface excess of calcium with respect to water, 
  and the ratios of the amount of calcium cations 
  bound to phosphate or carbonyl moieties 
  to the amount of such cations bound to both moieties in a POPC bilayer 
  from various simulation models. 
  $C_w$ is the concentration of CaCl$_2$ in water before adsorbing to the phospholipid bilayer. 
  \label{tab:binding}}
  \begin{tabular}{l|c | c c | c c}
    model                 & $\Gamma_{Ca}^w \,/\, \mathrm{nm}^{-2}$ & $C_{w}$ & $C_b\,/\,\mathrm{mM}$   & $r^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ & $r^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} $ \\
    \hline
    ECC-lipids            &  $0.06 \pm 0.01 $ &  350  &  $280\pm 10 $  &  99\%  &    25\%    \\
    Lipid14/\AA{}qvist    &  $0.13 \pm 0.01 $ &  350  &  $210\pm 10 $  & 100\%  &    37\%     \\
    Lipid14/Dang          &  $0.23 \pm 0.03 $ &  350  &  $160\pm 10 $  & 100\%  &    14\%    \\
    Lipid14/ECC-ions      &  $0.35 \pm 0.11 $ &  350  &  $120\pm 100$  & 100\%  &    23\%    \\
%Average no. of bound cations:
%L14+Aqvist: all:22.7, phos:22.7, carb:8.5
%L14+Dang:   all:29.2, phos:29.2, carb:4.0
%L14+ECC-ion:all:37.7, phos:37.7, carb:8.5
  \end{tabular}
\end{table}
